EvoSuite at the SBST 2015 Tool Competition

### 2015-02-19 papers/sbst15/paper_sbst15.tex
first complete draft

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
  %\scriptsize
\resizebox{0.9\textwidth}{!}{  
  \begin{tabular}{l rrrrrr} \toprule
Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
% Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch Coverage & Mutation Score \\ 
%Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
%Coverage & Mutation Score \\ 
%& Generation & Execution & & & & \\
\midrule
\input{results.tex}
\midrule
Average & & 371.58 & 2.10 & 55.36 & 47.19 & 41.02\\
\bottomrule
  \end{tabular}
}
\end{table*}

@@

Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18 classes, i.e. 28\% 
of the total.
For 14 of them (the 7 in the twitter4j and the 7 in the hibernate projects), this is due
to a mismatch in libraries on the classpath. 
In particular, \EVOSUITE does bytecode instrumentation using the ASM library.
However, the projects of the CUTs had their own (older) version of ASM.
This leads to errors like: ``java.lang.IncompatibleClassChangeError: 
class org.objectweb.asm.tree.ClassNode has interface org.objectweb.asm.ClassVisitor as super class''.
Note: \EVOSUITE can handle its own dependencies as CUTs, i.e. by using customized classloaders, 
but only during the search phase.
In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
even there (e.g., to support environment testing based on mock objects [TODO]).
So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
that thrown exception.
An easy solution would be to ship \EVOSUITE with its own ASM version using a 
different package name (e.g., by using the JarJar tool\footnote{https://code.google.com/p/jarjar/}).

For the other 4 classes, \EVOSUITE failed to generate any test. These are
\<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.

TODO

There are also cases of low coverage (e.g., less than 30\%).
For example, if look at line coverage, then 
we have \<Page> with 1.49\%, \<AbstractInstance> with 13.28\%, \<CategoryDescendantsIterator> with 8.24\%
and \<PageQueryIterable> with 18.57\%.

TODO

@@

>>>>

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
  %\scriptsize
\resizebox{0.9\textwidth}{!}{  
  \begin{tabular}{l rrrrrr} \toprule
Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
% Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch Coverage & Mutation Score \\ 
%Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
%Coverage & Mutation Score \\ 
%& Generation & Execution & & & & \\
\midrule
\input{results.tex}
\midrule
Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
\bottomrule
  \end{tabular}
}
\end{table*}

@@

Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18 classes, i.e. 28\% 
of the total.
For 14 of them (the 7 in the twitter4j and the 7 in the hibernate projects), this is due
to a mismatch in libraries on the classpath. 
In particular, \EVOSUITE does bytecode instrumentation using the ASM library.
However, the projects of the CUTs had their own (older) version of ASM.
This leads to errors like: ``java.lang.IncompatibleClassChangeError: 
class org.objectweb.asm.tree.ClassNode has interface org.objectweb.asm.ClassVisitor as super class''.
Note: \EVOSUITE can handle its own dependencies as CUTs, i.e. by using customized classloaders, 
but only during the search phase.
In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
even there (e.g., to support environment testing based on mock objects~\cite{arcuri2014automated}).
So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
that thrown exception.
An easy solution would be to ship \EVOSUITE with its own ASM version using a 
different package name (e.g., by using the JarJar tool\footnote{https://code.google.com/p/jarjar/}).

For the other 4 classes, \EVOSUITE failed to generate any test. These are
\<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.
There are also a further 4 cases of low coverage (e.g., less than 30\%).
For example, if look at line coverage, then 
we have \<Page> with 1.49\%, \<AbstractInstance> with 13.28\%, \<CategoryDescendantsIterator> with 8.24\%
and \<PageQueryIterable> with 18.57\%.
To improve \EVOSUITE, it will be important to understand why that was the case.

@@

With an overall score of $190.6$, \EVOSUITE achieved the second highest score of all tools in
the competition. The score calculated for best testing is $203.7$:  a very close
call. 
In particular, due to a configuration issue in the classpath of the target projects,
\EVOSUITE could had been run only on 7 out of 9 of the projects used as benchmark.
That is an easily fixed issue that would lead to even higher scores.
